GIVE ME A TITLE

### 2020-06-01 docs/article_bigsimr.tex
added references section

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={GIVE ME A TITLE},
  pdfauthor={A.G. Schissler; A.B. PERSON},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage[]{natbib}
\bibliographystyle{apalike}

@@

\begin{document}
\maketitle

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={GIVE ME A TITLE},
  pdfauthor={A.G. Schissler; A.B. PERSON},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{amsthm}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother
\usepackage[]{natbib}
\bibliographystyle{apalike}

@@

\begin{document}
\maketitle
\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum laoreet orci non elit fermentum mollis vel sit amet dolor. Proin ullamcorper, diam ac consectetur molestie, urna urna aliquet augue, sit amet vulputate felis massa ut libero. Integer mattis eget lorem vel viverra. Maecenas consequat feugiat mauris vitae porta. Mauris nec vulputate libero. Sed a turpis eget nisl tempus ultricies. Sed accumsan at augue a bibendum. Integer blandit, sem non imperdiet pharetra, tellus augue lobortis est, eget vestibulum massa ex eget purus. Suspendisse eleifend ullamcorper elit vitae pulvinar. Praesent vel tristique diam, vitae tempus leo. Nam placerat, massa a sodales porttitor, mauris felis ullamcorper eros, ut mattis lectus nisi vitae leo. Proin justo ante, fringilla quis consectetur at, euismod eget augue. In in nisi quis nunc fermentum semper ut a velit. Quisque suscipit dui in auctor tempor. Integer eu dui dictum, laoreet urna nec, tristique risus. Ut non tellus in metus.
\end{abstract}

@@

This is an example of a reference without braces \citet{xie2015} and a reference with braces \citep{xie2015}

### 2020-06-01 index.Rmd
added references section

--- 
title: "GIVE ME A TITLE"
author: [A.G. Schissler, A.B. PERSON]
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: article
bibliography: [bibliography.bib, packages.bib]
biblio-style: apalike
link-citations: yes
---

@@

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

@@

>>>>

--- 
title: "GIVE ME A TITLE"
author: [A.G. Schissler, A.B. PERSON]
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: article
bibliography: [bibliography.bib, packages.bib]
biblio-style: apalike
link-citations: yes
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum laoreet orci non elit fermentum mollis vel sit amet dolor. Proin ullamcorper, diam ac consectetur molestie, urna urna aliquet augue, sit amet vulputate felis massa ut libero. Integer mattis eget lorem vel viverra. Maecenas consequat feugiat mauris vitae porta. Mauris nec vulputate libero. Sed a turpis eget nisl tempus ultricies. Sed accumsan at augue a bibendum. Integer blandit, sem non imperdiet pharetra, tellus augue lobortis est, eget vestibulum massa ex eget purus. Suspendisse eleifend ullamcorper elit vitae pulvinar. Praesent vel tristique diam, vitae tempus leo. Nam placerat, massa a sodales porttitor, mauris felis ullamcorper eros, ut mattis lectus nisi vitae leo. Proin justo ante, fringilla quis consectetur at, euismod eget augue. In in nisi quis nunc fermentum semper ut a velit. Quisque suscipit dui in auctor tempor. Integer eu dui dictum, laoreet urna nec, tristique risus. Ut non tellus in metus.
---

@@

Remember each Rmd file contains one and only one chapter/section, and a chapter is defined by the first-level heading `#`.

@@

This is an example of a reference without braces @xie2015 and a reference with braces [@xie2015]
